Example Manuscript Template for a Data Analysis Project

### 2024-02-24 products/manuscript/Manuscript.qmd
Project Part 2 test

This study intends to identify distinct customer groups within sales data of luxury goods, with each group comprising customers who exhibit similar characteristics in terms of purchase frequency and amounts. Modeling customer spending as a mixture of gamma distributions helps to identify different spending behaviors. The objective is to develop an Expectation Maximization (EM) algorithm which segregates groups based on their spending patterns, considering the individual purchases transactions made by each customer.

@@

This study employs simulated data to assess the effectiveness of the EM algorithm. Following successful testing, the refined algorithm will be applied to actual sales data pertaining to luxury goods.

@@

This study aims to answer the question, "How effective is the Expectation Maximization (EM) algorithm in identifying distinct customer groups within luxury goods sales data when accounting for individual spending by each customer, as demonstrated by initial validation using simulated data?"

@@

@@

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results","height-weight-stratified.png"))
```

@@

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables-files","resulttable2.rds"))
knitr::kable(resulttable2)
```

>>>>

This study intends to identify distinct customer groups within sales data, with each group comprising customers who exhibit similar characteristics in terms of purchase frequency and amounts. Modeling customer spending as a mixture of gamma distributions helps to identify different spending behaviors. The objective is to develop an Expectation Maximization (EM) algorithm which segregates groups based on their spending patterns, considering the individual purchases transactions made by each customer.

The exploration begins with applying commonly used alternative models to a publicly available data and ultimately applying the gamma mixture model to this data.

@@

This study employs sales data, 'superstoredata' and focuses on international sales of the online retail store.

Initially this data was downloaded from Kaggle.com to it's usability for the project. Upon confirming the usability and revisiting the website seeking for further details, it could not be found in Kaggle.com. After few Google searches, the data and details were found on UC Irvine Machine Learning Repository [https://archive.ics.uci.edu/dataset/352/online+retail]. As per the website, this is a transnational data set containing all the transactions occurring between 12/1/2010 and 12/09/2011 for a UK-based and registered non-store online retail. The company primarily sells unique all-occasion gifts and many customers of the company are wholesalers.

This data has nine variables. The details are explained below:

(1)	InvoiceNo: It is a categorical variable with a 6-digit integral number uniquely assigned to each transaction. If this code starts with the letter ‘c’, it indicates a cancellation. 
(2)	StockCode: It is a categorical variable with a 5-digit integral number uniquely assigned to each distinct product.
(3)	Description: This represents Product name and is a categorical variable.
(4)	Quantity: It represents quantities of each product (item) per transaction and is an integer.
(5)	InvoiceDate: It represents the day and time each transaction was generated.
(6)	UnitPrice: It represents product price per unit in sterling.
(7)	CustomerID: It is a categorical variable with a 5-digit integral number uniquely assigned to each customer.
(8)	Country: It represents the name of the country where each customer resides.

The study will also use simulated data to formulate the EM algorithm. Following successful testing, the refined algorithm will be applied to the sales data.

@@

This study aims to answer the question, "How effective is the Expectation Maximization (EM) algorithm in identifying distinct customer groups when accounting for individual spending by each customer, as demonstrated by initial validation using simulated data?"

@@

This study employs sales data, 'superstoredata' and focuses on international sales of the online retail store.

Initially this data was downloaded from Kaggle.com to it's usability for the project. Upon confirming the usability and revisiting the website seeking for further details, it could not be found in Kaggle.com. After few Google searches, the data and details were found on UC Irvine Machine Learning Repository [https://archive.ics.uci.edu/dataset/352/online+retail]. As per the website, this is a transnational data set containing all the transactions occurring between 12/1/2010 and 12/09/2011 for a UK-based and registered non-store online retail. The company primarily sells unique all-occasion gifts and many customers of the company are wholesalers.

This data has nine variables. The details are explained below:

(1)	InvoiceNo: It is a categorical variable with a 6-digit integral number uniquely assigned to each transaction. If this code starts with the letter ‘c’, it indicates a cancellation. 
(2)	StockCode: It is a categorical variable with a 5-digit integral number uniquely assigned to each distinct product.
(3)	Description: This represents Product name and is a categorical variable.
(4)	Quantity: It represents quantities of each product (item) per transaction and is an integer.
(5)	InvoiceDate: It represents the day and time each transaction was generated.
(6)	UnitPrice: It represents product price per unit in sterling.
(7)	CustomerID: It is a categorical variable with a 5-digit integral number uniquely assigned to each customer.
(8)	Country: It represents the name of the country where each customer resides.

The study will also use simulated data to formulate the EM algorithm. Following successful testing, the refined algorithm will be applied to the sales data.

@@

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("results", "figures", "Sales_distribution.png"))
```

@@

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
resulttable2 = readRDS(here("results","tables","summarytable.rds"))
knitr::kable(resulttable2)
```
